\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Portfolio 1 - Dota Stats Requirements Document}
\date{April 2025}

\begin{document}

\maketitle

\section{Project Team}

\begin{itemize}
    \item David David-Iulian Springean (david-iulian.springean@study.thws.de) Immatriculation Number
    \item Dzmitry Karobka (dzmitry.karobka@study.thws.de) Immatriculation Number
    \item Artur Denislamov (artur.denislamov@study.thws.de) Immatriculation Number
\end{itemize}

\section{Project Overview}

\section{Key Features}
A list of major features to be implemented and prioritized with indications of "must-have" vs. "nice-to-have."

\section{User Roles and Interactions}
Description of different types of users (e.g., admin,
student, customer). Typical user actions and expected outcomes.

\section{User Stories or Use Cases}
At least 5-7 detailed user stories or structured use cases.
Should reflect the real interaction flow in the application

\section{Non-Functional Requirements}
Expectations for usability, responsiveness, accessibility, performance, etc. The user interface design is not part of this document.

\section{Technology Assumptions}
Any known frameworks or technical approaches your group
is planning to use. Please note that you must use the React framework for Web development. The backend can be developed using any technology. Using REST APIs is
preferred.

\section{Project Constraints}
How to create small yet efficient backend for caching and calculating required data? 
Do we need cookies for saving user tracked playerIDs?
With which algorithm should be determine high-winrate items and item combinations?

\section{AI Usage Description}
Document should be \textbf{human-written}


\end{document}
