\section{Key Features}

\subsection{Must-have features}

\subsubsection{Player's Profile}

\begin{itemize}

    \item Display player's match history with heroes, player's KDA, match duration and result (win/lose).
    Display overall win rate, win rate on each played hero, most efficient hero, current rank.
    \item Give a user an option to store preferred profile IDs in cookies, so it's not necessary to type ID each type.

\end{itemize}

\subsubsection{Hero's Stats}

\begin{itemize}

    \item Show all heroes with their win, pick and ban rates.
    \item Allow user to sort list of heroes based on one of these values.
    \item Give option to choose ELO range for these stats.

\end{itemize}

\subsubsection{Selected Hero Stats and Itemization}

\begin{itemize}

    \item When hero is selected, display the best items for it.
    Analyze matches' data and determine these items (custom algorithm required).

\end{itemize}

\subsubsection{Other data}

\begin{itemize}

    \item Display rank distributions histogram (number of players per ELO range).

\end{itemize}


\subsection{Nice-to-have features}

\begin{itemize}

    \item Display player's rank history graph, wins/loses histogram and other possible graphs.
    \item Display player's ward map (heat map of placed wards).
    \item Display professional teams current ELO ranking with number of wins and losses.
    \item Display separate page for each finished match with match-specific data (heroes, items, timings, etc.).
    \item Show base characteristics for each selected hero (wiki information, like attack speed, move speed, etc.).

\end{itemize}

