\section{Summary of Requirements}

This section summarizes the core functional and non-functional requirements for the \textit{Dota Stats} web application. These requirements form the basis for the design, implementation and evaluation of the application.

\subsection{Functional Requirements}

\begin{itemize}
    \item \textbf{Player Profile Search}
    \begin{itemize}
        \item Users can search for a Dota 2 player by entering a player ID.
        \item Display match history including hero played, match result, and duration.
        \item Show win rate overall and by hero, most efficient hero, and current rank.
    \end{itemize}

    \item \textbf{Hero Statistics}
    \begin{itemize}
        \item List all heroes with their win and pick rates based on overall range, and different rank ranges.
        \item Support sorting by each of these statistics.
    \end{itemize}

    \item \textbf{Hero Matrix}
    \begin{itemize}
        \item Interactive matrix showing all heroes based on four categories (strength, agility, intelligence and universal).
        \item Users can click on any hero to open a detailed screen of the selected hero.
    \end{itemize}


    \item \textbf{Selected Hero Analysis}
    \begin{itemize}
        \item Show suggested item builds for start game, early game, mid game and late game.
        \item Display base characteristics of selected heroes (e.g., health, mana, movement speed).
        \item Provide hero matchup information.
        \item Hovering over items display item cost and characteristics.
    \end{itemize}
\end{itemize}

\subsection{Non-Functional Requirements}

\begin{itemize}
    \item \textbf{Usability}
    \begin{itemize}
        \item Interface should be intuitive with minimal need for instructions.
        \item Important data should be easy to find and interpret.
    \end{itemize}

    \item \textbf{Performance}
    \begin{itemize}
        \item Fast response time for searches and data visualizations.
        \item Smooth rendering even with large datasets.
    \end{itemize}

    \item \textbf{Responsiveness}
    \begin{itemize}
        \item Layout and components must adapt to different screen sizes.
    \end{itemize}

    \item \textbf{Accessibility}
    \begin{itemize}
        \item Conform to WCAG 2.1 guidelines.
        \item Ensure legible color contrast.
    \end{itemize}

    \item \textbf{Technical Stack Assumptions}
    \begin{itemize}
        \item React, Tailwind CSS, Vite.
        \item Data from OpenDota API.
    \end{itemize}
\end{itemize}